Midterm Review Questions

### 2019-10-10 static/slides/midterm-review.Rmd
Tweak review slides

- What are the four assumptions we make about the error term?
- Which is most important?

@@

- What is in $u_i$?

- Is $\hat{\beta_1}$ likely biased?

@@

- What does $R^2$ measure? What does it mean? How do we calculate it?

@@

- What does $\sigma_u$ (SER) measure? What does it mean?

@@

- Interpret all of these numbers (except Adjusted R-squared and the last line):

@@

- Interpret all of these numbers (except Adjusted R-squared and the last line):

@@

- Suppose $Y$ is normally distributed with a mean of 10 and a standard error of 5. What is the probability that $Y$ is between 5 and 15?

@@

- Explain what a $Z$-score means.

@@

- Explain what a $p$-value means. :)

@@

- We run the following hypothesis test at $\alpha=0.05$:

@@

- Is this test one-sided or two-sided?

- We find the $p$-value is 0.02. What is our conclusion? Be specific and precise in your wording!

>>>>

What are the four assumptions we make about the error term?

Which is most important?

@@

What is in $u_i$?

Is $\hat{\beta_1}$ likely biased?

@@

What does $R^2$ measure? What does it mean? How do we calculate it?

@@

What does $\sigma_u$ (SER) measure? What does it mean?

@@

Interpret all of these numbers (except Adjusted R-squared and the last line):

@@

Interpret all of these numbers:

@@

Suppose $Y$ is normally distributed with a mean of 10 and a standard error of 5. What is the probability that $Y$ is between 5 and 15?

@@

Explain what a $Z$-score means.

@@

Explain what a $p$-value means. :)

@@

We run the following hypothesis test at $\alpha=0.05$:

@@

Is this test one-sided or two-sided?

We find the $p$-value is 0.02. What is our conclusion? Be specific and precise in your wording!
